A Data-Driven Framework for Neural Field Modeling

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{soul}
\usepackage{anysize} %<-for setting margins
\marginsize {1.6cm}{1.6cm}{2.0cm}{2cm}
\usepackage{color}
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

    \section{Reviewer 2}

    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.\\

	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model. The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data. While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent. Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}
	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
 \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
r,t)}{dt}+\zeta^2v(\mathbf r,t)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
\mathbf{r}',t \right) \right)d\mathbf{r}'} 
\end{equation}
and in a discretized form we have
\begin{equation}
 v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
\end{equation}}}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

    \subsection{Additional Comments}

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  in a worst case scenario if we assume $f(v_t(\mathbf r))$ saturates for all $g_t$ we have
		  \begin{align}
		   g_{t}(\mathbf r)=&\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)d\mathbf{r}'} \nonumber \\
				   =-a
		  \end{align}	
		  where $a$ is the area under the connectivity kernel. Substituting $-a$ for all $g_{t}$ in \eqref{vrecursive} we get
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-aT_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit}
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{a}{\zeta}
		  \end{equation}
		  by choosing sufficiently small $T_s$ the discretized model will be stable.}}

@@

    \section{Reviewer 2}

    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.\\

	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model. The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data. While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent. Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}
	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
 \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
r,t)}{dt}+\zeta^2v(\mathbf r,t)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
\mathbf{r}',t \right) \right)d\mathbf{r}'} 
\end{equation}
and in a discretized form we have
\begin{equation}
 v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)= T_s^2\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
\end{equation}}}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  in a worst case scenario if we assume $f(v_t(\mathbf r))$ saturates for all $g_t$ we have
		  \begin{align}
		   g_{t}(\mathbf r)=&\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)d\mathbf{r}'} \nonumber \\
				   =-a
		  \end{align}	
		  where $a$ is the area under the connectivity kernel. Substituting $-a$ for all $g_{t}$ in \eqref{vrecursive} we get
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-aT_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{a}{\zeta}
		  \end{equation}
		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
		  if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{g_{b}}{\zeta}
		  \end{equation}
		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{g_{b}}{\zeta}
		  \end{equation}
		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written in a form of 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)+g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{b}}{\zeta}
		  \end{equation}
		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}

		\emph{We should add some more to the modeling assumptions section to address this one. I have begun to talk about the LL method. \parham{here he just ask about Euler method he doesn't ask about s-word.}}

### 2011-01-09 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\

		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written in a form of 
		  \begin{equation}\label{vrecursive}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
		  \end{equation}
		  where
		  \begin{equation}
		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
\mathbf{r}'\right) \right)d\mathbf{r}'} 
		  \end{equation}
		  since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
		  \begin{align}\label{vrecursiveinlimit}
		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)+g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
				     &=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
		  \end{align}
		  in a limit equation (geometric series) \eqref{vrecursiveinlimit} can be written as 
		  \begin{equation}\label{simplifiedvrecursiveinlimit}
		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s}{1-\xi}
		  \end{equation}
		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
		  \begin{equation}
		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{b}}{\zeta}
		  \end{equation}
		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}

### 2011-01-09 ltx/first_order_framework/LaTeX_Manuscript.tex
added stability proof to appendix from Parhams derivation

>>>>

Even though the continuous system is stable, it is not guaranteed the discrete system is stable when using Euler's method. Therefore, it is necessary to demonstrate the stability of the discretized IDE. To show this, the model is written as the series
\begin{align}
	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \\
	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
\end{align}
where
\begin{equation}
	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
\end{equation}
Now, since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded. To assess the stability of the system  we assume the entire field is firing at the maximal rate. Therefore $g_{t}(\mathbf{r}) = c$, where $c$ is the integral of the connectivity kernel. Substituting this into equation~\ref{eq:fieldmodelseries} yields
\begin{align}\label{vrecursiveinlimit}
	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ c T_s \sum_{i=0}^t \xi^i \nonumber \\
	&=\xi^{t+1}v_0(\mathbf r) + \frac{ c T_s(1-\xi^{t+1})}{1-\xi}.
\end{align}
Now considering the limit as $t$ approaches infinity, equation \eqref{vrecursiveinlimit} can be written as a geometric series
\begin{equation}\label{simplifiedvrecursiveinlimit}
	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{c T_s}{1-\xi}.
\end{equation}
Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
\begin{equation}
	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{c}{\zeta}.
\end{equation}
From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$. The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$. Therefore, the discretization preserved the stability properties of the system.
